---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include=F}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Long Term Care Facility COVID Dashboard

<!-- badges: start -->
<!-- badges: end -->

The goal of LTCF Covid Dashboard is to provide a tool for Long Term Care Facility
staff and stakeholders to explore the spread of COVID-19 with in long term care
facilities and the effects of variables like vaccination rates, community prevalence, 
and testing cadence. 

More information on this tool and it's implications can be found at 
[Link to paper](https://github.com/jakedilliott/ltcf_covid_dashboard)

# File structure
```
ltcf_covid_dashboard
├── LICENSE
├── R
│   ├── 00_project_init.R
│   ├── 01_abm_helpers.R
│   ├── 02_abm_fun.R
│   ├── 03_plot_funs.R
│   ├── 04_summaries.R
│   └── 05_splash_page.R
├── README.md
├── README.Rmd
├── server.R
├── ui.R
└── www
    └── styles.css
```

# Running the app locally

__Required Packages__ :

shiny, shinyDashboard, tidyr, dplyr, purrr, ggplot2, conflicted, plotly

## Using `runGitHub` from the shiny package

This requires the [Shiny](https://www.github.com/rstudio/shiny) package. 
```{r, eval=F}
if (!require("shiny", character.only = TRUE)) {
  install.packages("shiny", dependencies = TRUE)
}
library(shiny)
runGitHub("jakedilliott/ltcf_covid_dashboard")
```

## Running the files on your local machine

1. clone or download this repository from GitHub
2. open the folder in RStudio and run the app by opening the __ui.R__ file and pressing the __runApp__ button or typing `shiny::runApp()` into the console. For the second option make sure the working directory is set to ltcf_covid_dashboard.

# Running your own simulations 

1. Source files in the __R/__ directory, which holds all of the agent-based model simulation functions
2. Initialize agents that will be used in the simulation with the `make_agents()` function (found in R/01_abm_helpers.R)
3. Use the `snf_abm()` function to run simulations. Read R/02_abm_fun.R to see the inputs for the `snf_abm()` function. For running multiple simulations there is also the `multi_run()` function which takes the number of simulations you want to run and all of the same inpunts as `snf_abm()`

## Minimal Example

```{r, eval=F}
# Source files in R/ directory
files <- list.files("R/", full.names = TRUE)
lapply(files, source, echo = FALSE)

# Example simulation with 125 Day Staff, 45 Night staff, and 90 Residents
# 38% of Staff are vaccinated, 78% of Residents are vaccinated
# start the simulation with 2% of staff infected
# The rest of the inputs are left to their defaults, 
# which can be found in R/02_abm_fun.R
agents <- make_agents(day = 125, night = 45, res = 90)
sim_results <- snf_abm(inputs = agents, R_0_staff = 0.38, R_0_res = 0.78,
                       init_inf_staff = 0.02)
```
